A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-07 main.tex
Cut some more stuff

We implement a calculus for Parikh automata as described in
\cref{sec:parikh-automata}. The artefact submitted along with this paper
is a program that reads one or more products of one or more DFA, the register
incrementations performed along the edges of their transitions, and the labels
of the transitions as ranges of Unicode characters, along with a set of
constraints on the final values of their registers expressed as Presburger
arithmetic. We call this program \Catra.\footnote{If you really must read it
as an acronym, please read it as CAtegory Theory on Register Automata, or if you
object to the somewhat nonstandard use of register automata and category theory,
as Check Assignments of The Registers Afterwards, or alternatively if you find it
all to be too much of a theoretical exercise as Can Anyone Think of A Real
Application.}

>>>>

We implement \Calculus{} for Parikh automata as described in
\cref{sec:parikh-automata}. The artefact submitted along with this paper is a
program that reads an instance file with one or more products of one or more
Parikh automaton with transition labels defined as ranges of Unicode characters,
along with a set of constraints on the final values of their registers expressed
as Presburger arithmetic in a C-like syntax. We call this program
\Catra.\footnote{If you really must read it as an acronym, please read it as
CAtegory Theory on Register Automata, or if you object to the somewhat
nonstandard use of register automata and category theory, as Check Assignments
of The Registers Afterwards. Or alternatively if you find it all to be too much
of a theoretical exercise, as Can Anyone Think of A Real Application.}
